A Context Menu for the Real World: Controlling Physical Devices Through Head-Worn Infrared Targeting

### 2013-09-18 doc/sigchi14/interaction.tex
remove old figure syntax
moved the figure
current status of the appliance is retreived by Glass and shown on the UI
1. update figure and caption 2. note that system retrieves appliance status

These design goals find their expression in the following interaction model:

% \begin{figure}[t!]
% \centering
% \includegraphics[width=0.5\columnwidth]{figures/screenshot_LAMP_CONTROL.png}
% \caption{ }
% \label{fig:control_lamp}
% \end{figure}

% \begin{figure}[t!]
% \centering
% \includegraphics[width=0.5\columnwidth]{figures/screenshot_TV_CONTROLS.png}
% \caption{( devices. }
% \label{fig:control_tv}
% \end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/stepbystep_multi.png}
\caption{When multiple clients are within range, they would all have red LEDs illuminated for feedback (A). Users call up the disambiguation where all responding clients lights up blue LED while the current hovered one blinks (B). Swiping the touchpad is to traverse among responding devices (C).}
\label{fig:interaction_multi}
\end{figure}

@@

{\bf Control:} Glass displays a user interface for parameters of the chosen device. The interface is controlled with the temple-mounted touchpad through the following gesture set: tapping toggles discrete parameters (such as power for a lamp as Figure~\ref{fig:control_lamp}); single finger swipe changes between available parameters; double finger swipe adjusts continuous parameters (such as volume for a video player as Figure~\ref{fig:control_tv}). This scheme was chosen because the touchpad is only comfortably operable in the coronal plane (front to back) but not in the saggital plane (up and down). 
Control commands are sent over XBee radios.

>>>>

These design goals find their expression in the following interaction model.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/stepbystep_multi.png}
\caption{When multiple clients are within range, they would all have red LEDs illuminated for feedback (A). Users call up the disambiguation where all responding clients lights up blue LED while the current hovered one blinks (B). Swiping on the touchpad to traverse among responding devices (C).}
\label{fig:interaction_multi}
\end{figure}

@@

{\bf Control:} Glass displays a user interface for parameters of the chosen device. Upon connected, the current status of the appliance is retreived by Glass and shown on the UI. The interface is controlled with the temple-mounted touchpad through the following gesture set: tapping toggles discrete parameters (such as power for a lamp as Figure~\ref{fig:control_lamp}); single finger swipe changes between available parameters; double finger swipe adjusts continuous parameters (such as volume for a video player as Figure~\ref{fig:control_tv}). This scheme was chosen because the touchpad is only comfortably operable in the coronal plane (front to back) but not in the saggital plane (up and down). 
Control commands are sent over XBee radios.
